Software Frameworks for Deep Learning at Scale

### 2016-07-29 report/Report/para/1-introduction.tex
added new line to comparison chart: deep learning models

The goal of this paper is to survey the landscape of deep learning frameworks with full support for parallelization. Three levels of parallelization exist on the hardware level: within a GPU, between GPUs on a single node, and between nodes. Two forms of parallelism also exist on the application level: model and data parallelism. Other aspects of frameworks include release date, core language, user-facing API, computation model, communication model, programming paradigm, fault tolerance, and visualization. This choice of criteria is explained in detail in Section 2. Tensorflow, CNTK, Deeplearning4j, MXNet, H2O, CaffeOnSpark, Theano, and Torch do not necessarily encompass the entire space of frameworks for deep learning. However, these were chosen by a combination of factors, including their being open-source, level of documentation, maturity as a complete product, and level of adoption by the community. These frameworks, as well as some others not included in the Section 2 chart, are examined in detail in Section 3. Additional comments regarding parallelism in deep learning, as well as scalability, are also discussed at the end of Section 3. Section 4 concludes the paper.

>>>>

The goal of this paper is to survey the landscape of deep learning frameworks with full support for parallelization. Three levels of parallelization exist on the hardware level: within a GPU, between GPUs on a single node, and between nodes. Two forms of parallelism also exist on the application level: model and data parallelism. Other aspects of frameworks include release date, core language, user-facing API, computation model, communication model, programming paradigm, fault tolerance, and visualization. This choice of criteria is explained in detail in Section 2. Tensorflow, CNTK, Deeplearning4j, MXNet, H2O, CaffeOnSpark, Theano, and Torch do not necessarily encompass the entire space of frameworks for deep learning, but were selected by a combination of factors: their being open-source, level of documentation, maturity as a complete product, and level of adoption by the community. These frameworks, as well as some others not included in the Section 2 chart, are examined in detail in Section 3. Section 4 discusses finer points of parallelism and scalability in deep learning which may escape but are pertinent to the framework discussion. Section 5 offers concluding remarks.

### 2016-07-29 report/Report/para/2-comparison.tex
added new line to comparison chart: deep learning models

\section{Framework Comparison}
\begin{table*}
\small
\centering
\caption{Open-source Frameworks}
\resizebox{\textwidth}{!}{
    \begin{tabular}{|m{2cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|m{2cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|m{1.7cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|}
    \hline
    Platform & Tensorflow & CNTK & Deeplearning4j & MXNet & H2O & CaffeOnSpark & Theano & Torch \\ \hline\hline
    Release Date & 2016 & 2016 & 2015 & 2015 & 2014 & 2016 & 2010 & 2011 (deep learning) \\
    \hline
    Core Language & C++  & C++ & Java  & C++ & Java & C++, Scala & C++ & C \\
    \hline
    API & C++, Python & NDL & Java, Scala & C++, Python, R, Scala, Matlab, Javascript, Go, Julia & Java, R, Python, Scala, Javascript, web-UI & Python, Matlab, Scala & Python & Lua \\
    \hline
    Synchronization Model & Sync or async & Sync & Sync & Sync or async & Async & Sync & Async & Sync \\
    \hline
    Communication Model & Parameter server & MPI & Iterative MapReduce & Parameter server & Distributed fork-join & MPI Allreduce & N/A & N/A \\
    \hline
    Multi-GPU & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark \\
    \hline 
    Multi-node & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark & \xmark \\
    \hline
    Data Parallelism & \cmark & \cmark & \cmark & \cmark& \cmark & \cmark & \cmark & \cmark \\
    \hline
    Model Parallelism & \cmark & N/A & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark \\
    \hline
    Programming Paradigm & Imperative & Imperative & Declarative & Both & Declarative & Declarative & Imperative & Imperative \\
    \hline
    Fault Tolerance & Checkpoint-and-recovery & Checkpoint-and-resume & Checkpoint-and-resume & Checkpoint-and-resume & N/A & N/A & Checkpoint-and-resume & Checkpoint-and-resume \\
    \hline
    Visualization & Graph (interactive), training monitoring & Graph (static) & Training monitoring & None & None & Summary Statistics & Graph (static) & Plots \\
    \hline
    \end{tabular}
}
\end{table*}

@@

The communication model tries to categorize the nature of distributed execution by well-known paradigms.

>>>>

\section{Framework Comparison}
\begin{table*}
\small
\centering
\caption{Open-source Frameworks}
\resizebox{\textwidth}{!}{
    \begin{tabular}{|m{2cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|m{2cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|m{1.7cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|}
    \hline
    Platform & Tensorflow & CNTK & Deeplearning4j & MXNet & H2O & CaffeOnSpark & Theano & Torch \\ \hline\hline
    Release Date & 2016 & 2016 & 2015 & 2015 & 2014 & 2016 & 2010 & 2011 (deep learning) \\
    \hline
    Core Language & C++  & C++ & Java  & C++ & Java & C++, Scala & C++ & C \\
    \hline
    API & C++, Python & NDL & Java, Scala & C++, Python, R, Scala, Matlab, Javascript, Go, Julia & Java, R, Python, Scala, Javascript, web-UI & Python, Matlab, Scala & Python & Lua \\
    \hline
    Synchronization Model & Sync or async & Sync & Sync & Sync or async & Async & Sync & Async & Sync \\
    \hline
    Communication Model & Parameter server & MPI & Iterative MapReduce & Parameter server & Distributed fork-join & MPI Allreduce & N/A & N/A \\
    \hline
    Multi-GPU & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark \\
    \hline 
    Multi-node & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark & \xmark \\
    \hline
    Data Parallelism & \cmark & \cmark & \cmark & \cmark& \cmark & \cmark & \cmark & \cmark \\
    \hline
    Model Parallelism & \cmark & N/A & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark \\
    \hline
    Model Parallelism & \cmark & N/A & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark \\
    \hline
    Deep Learning Models & DBN, CNN, RNN & DBN, CNN, RNN & DBN, CNN, RNN & DBN, CNN, RNN & DBN & DBN, CNN, RNN & DBN, CNN, RNN & DBN, CNN, RNN \\
    \hline
    Programming Paradigm & Imperative & Imperative & Declarative & Both & Declarative & Declarative & Imperative & Imperative \\
    \hline
    Fault Tolerance & Checkpoint-and-recovery & Checkpoint-and-resume & Checkpoint-and-resume & Checkpoint-and-resume & N/A & N/A & Checkpoint-and-resume & Checkpoint-and-resume \\
    \hline
    Visualization & Graph (interactive), training monitoring & Graph (static) & Training monitoring & None & None & Summary Statistics & Graph (static) & Plots \\
    \hline
    \end{tabular}
}
\end{table*}

@@

The communication model tries to categorize the nature of across-machine execution according to well-known paradigms.
